Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-13 paper/paper.tex
Temporarily force refs onto new page, so we can see how much room we have
Thanks Frances
We have the proofs

@@

@@

% \section*{Acknowledgements}

% Other stuff to stick back in: proofs, example of paths of length 3, correlation heatmap

>>>>

\usepackage{placeins}

@@

        \begin{scope}[xshift=-1cm, yshift=-3cm, color=black]
        \node at (-1,0) {$P$:};
        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
        \node [fill, circle, inner sep=1.5pt] (b) at (1,-1) {};
        \node [fill, circle, inner sep=1.5pt] (c) at (1,0) {};
        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
        \node [fill, circle, inner sep=1.5pt] (e) at (2,0) {};
        \node [fill, circle, inner sep=1.5pt] (f) at (3,0) {};
        \node[draw=none,below of = e,node distance=3mm,anchor=base] {$p$};

        \path[solid] (a) edge (b) edge (c) edge (d)
            (b) edge (e)
            (c) edge (e)
            (d) edge (e)
            (e) edge (f);
        \end{scope}

        \begin{scope}[xshift=6cm, yshift=-3cm, color=black]
        \node at (-1,0) {$T$:};
        \node [fill, circle, inner sep=1.5pt] (a) at (0,0) {};
        \node [fill, circle, inner sep=1.5pt] (b) at (1,-1) {};
        \node [fill, circle, inner sep=1.5pt] (c) at (1,0) {};
        \node [fill, circle, inner sep=1.5pt] (d) at (1,1) {};
        %\node [fill, circle, inner sep=1.5pt] (e) at (2,0) {};
        \node [fill, circle, inner sep=1.5pt] (f) at (3,0) {};

        \path[solid] (a) edge (b) edge (c) edge (d);
        %    (b) edge (e)
        %    (c) edge (e)
        %    (d) edge (e)
        %    (e) edge (f);
        \end{scope}

    \end{tikzpicture}
    \caption{The pattern graph $P$ on the left cannot be found in the target graph $T$, but if
    the vertex $p$ in $P$ is removed, then a subgraph isomorphism exists.}
    \label{figure:pathlength3example}
\end{figure}

@@

\section*{Acknowledgements}

We would like to thank Frances Cooper for her comments.

% Other stuff to stick back in: example of paths of length 3, correlation heatmap

\FloatBarrier
\clearpage
